---
title: "Apply statcheck to assignments"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Dependencies

```{r}

library(dplyr)
library(statcheck)
library(janitor)
library(stringr)
library(tidyr)
library(knitr)
library(kableExtra)
library(readr)

```

# Summarize results

```{r}

dat <- read_csv("statcheck results assignments.csv") |>
  janitor::clean_names() |>
  fill(doi, .direction = "down") |>
  fill(researcher, .direction = "down") |>
  filter(statistic != "Statistic" & !is.na(statistic)) |>
  mutate(correct = tolower(correct)) |>
  mutate(correct = str_replace(correct, "✓", "yes"),
         correct = str_replace(correct, "incorrect", "no"),
         correct = str_replace(correct, "correct", "yes")) 


dat |>
  distinct(researcher, doi) |>
  write_csv("researcher_and_doi_for_future_assignment_on_misinterpretations_of_p_values.csv")

dat |> 
  mutate(error = case_when(correct == "no" ~ "no",
                           TRUE ~ "other")) |>
  count(error, name = "n_tests") |>
  mutate(percent = janitor::round_half_up(n_tests/sum(n_tests)*100, 1)) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

dat |> 
  group_by(doi) |>
  summarize(any_error = any(correct == "no", na.rm = TRUE)) |>
  ungroup() |>
  count(any_error, name = "n_articles") |>
  mutate(percent = janitor::round_half_up(n_articles/sum(n_articles)*100, 1)) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)



# dat |> 
#   filter(statistic != "no results are detected") |>
#   mutate(error = case_when(correct == "no" ~ "no",
#                            TRUE ~ "other")) |>
#   count(error, name = "n_tests") |>
#   mutate(percent = janitor::round_half_up(n_tests/sum(n_tests)*100, 1)) |>
#   kable(align = "r") |>
#   kable_classic(full_width = FALSE)
# 
# dat |> 
#   filter(statistic != "no results are detected") |>
#   group_by(doi) |>
#   summarize(any_error = any(correct == "no", na.rm = TRUE)) |>
#   ungroup() |>
#   count(any_error, name = "n_articles") |>
#   mutate(percent = janitor::round_half_up(n_articles/sum(n_articles)*100, 1)) |>
#   kable(align = "r") |>
#   kable_classic(full_width = FALSE)

```

Visual inspection of `dat` shows no decision errors.

# Critique of this analysis

What could go wrong here? Why might these results be wrong or incomplete?

- Incomplete extractions. Results were extracted automatically. It could have made errors or missed the results of additional tests.
- Failing to detect one-sided tests.

# Session info

```{r}

sessionInfo()

```



