---
title: "Extending Fried & Kievit's (2016) simulation critiquing Schmaal et al. (2016)"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set default chunk options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

```{r}

# dependencies
library(ggplot2)
library(dplyr)
library(tidyr)
library(tibble)
library(purrr)
library(janitor)
library(plotrix) # for std.error
library(knitr)
library(kableExtra)

```

# Visualising effect size reported in Schmaal

Overall sample result in original publication: Cohen's d = .144, 95% CI [.064, .225]. N control = 7040, N MDD = 1700 (see Schmaal et al., 2016 table 1).

```{r}

ggplot(data = data.frame(x = c(-4, 4)), aes(x = x)) +
  stat_function(
    fun = dnorm, 
    args = list(mean = 0, sd = 1), 
    color = "blue", 
    size = 1
  ) +
  stat_function(
    fun = dnorm, 
    args = list(mean = 0.144, sd = 1), 
    color = "red", 
    size = 1
  ) +
  labs(
    title = "Point estimate (Cohen's d = .144)",
    x = "Hippocampal volume (standardized)",
    y = "Density"
  ) +
  theme_linedraw()

ggplot(data = data.frame(x = c(-4, 4)), aes(x = x)) +
  stat_function(
    fun = dnorm, 
    args = list(mean = 0, sd = 1), 
    color = "blue", 
    size = 1
  ) +
  stat_function(
    fun = dnorm, 
    args = list(mean = 0.064, sd = 1), 
    color = "red", 
    size = 1
  ) +
  labs(
    title = "Lower bound CI (Cohen's d = .064)",
    x = "Hippocampal volume (standardized)",
    y = "Density"
  ) +
  theme_linedraw()

ggplot(data = data.frame(x = c(-4, 4)), aes(x = x)) +
  stat_function(
    fun = dnorm, 
    args = list(mean = 0, sd = 1), 
    color = "blue", 
    size = 1
  ) +
  stat_function(
    fun = dnorm, 
    args = list(mean = 0.225, sd = 1), 
    color = "red", 
    size = 1
  ) +
  labs(
    title = "Lower bound CI (Cohen's d = .225)",
    x = "Hippocampal volume (standardized)",
    y = "Density"
  ) +
  theme_linedraw()

```

# Simulate classification accuracy implied by Schmaal's effect size

Fried & Kievit (2016) reported a classification accuracy of 52.6% but using just a single simulated data set and no set seed (i.e. re-running their code produces different results). I therefore replicated their simulation and increased the number of iterations to average over to 1000.

```{r}

set.seed(42)

generate_data <- function(n_control, 
                          n_mdd,
                          population_cohens_d) {
  
  require(dplyr)
  require(tibble)
  
  data <- 
    bind_rows(
      tibble(condition = "control",
             hippocampal_volume = rnorm(n = n_control, mean = 0, sd = 1)),
      tibble(condition = "mdd",
             hippocampal_volume = rnorm(n = n_mdd, mean = population_cohens_d, sd = 1))
    ) |>
    mutate(condition_numeric = case_when(condition == "control" ~ 1,
                                         condition == "mdd" ~ 2))
  
  return(data)
}

analyse <- function(data) {
  
  require(yardstick)
  require(mclust)
  
  fit <- mclust::Mclust(data = data$hippocampal_volume, 
                        G = 2, # two clusters
                        verbose = FALSE) 
  
  classifications <- tibble(truth = factor(data$condition_numeric),
                            estimate = factor(fit$classification))
  
  res <- yardstick::accuracy(classifications, 
                             truth = truth, 
                             estimate = estimate) |>
    select(accuracy = .estimate)
  
  return(res)
}

simulation <- 
  # "using the experiment parameters..."
  expand_grid(n_control = 7040,
              n_mdd = 1700,
              population_cohens_d = c(.144, .064, .225), 
              iteration = 1:1000) |>
  
  # ...generate data that meets those parameters...
  mutate(data = pmap(list(n_control, 
                          n_mdd,
                          population_cohens_d),
                     generate_data)) |>
  
  # "... then apply the analysis function to the generated data using the parameters relevant to analysis"
  mutate(results = pmap(list(data), 
                        analyse))

# summarize across iterations
simulation_results <- simulation |>
  unnest(results) |>
  group_by(n_control,
           n_mdd,
           population_cohens_d) |>
  summarize(classification_accuracy_mean = mean(accuracy),
            classification_accuracy_se = std.error(accuracy),
            .groups = "drop") |>
  select(n_control, n_mdd, population_cohens_d,
         classification_accuracy_mean,
         classification_accuracy_se) 

# print table
simulation_results |>
  mutate_if(is.numeric, round_half_up, digits = 3) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)


res_string <- paste0(
  "Classification accuracy = ", simulation_results$classification_accuracy_mean[2] |> round_half_up(3), 
  ", 95% CI [", simulation_results$classification_accuracy_mean[1] |> round_half_up(3), 
  ", ", simulation_results$classification_accuracy_mean[3] |> round_half_up(3), "]"
)

# res_string

```

Results of this simulation, simulating classification accuracy for Schmall et al.'s (2015) point estimate of Cohen's d but also their CIs: `r res_string`

Note that [Bartoš et al. (2023)](https://arxiv.org/abs/2310.04153), after flipped coins 350,757 times and found that the probability of a flipped coin landing on the same side has a slight bias: 50.8%. The probability of being able to predict whether a given person has MDD is therefore not merely akin to tossing a coin, it is statistically comparable to it, given the bias of tossed coins.

Cost of just the MRI scans for this study can be roughly estimated at `r 8159 * 1000` CHF.

Citations in 2024/11: 

- Schmaal et al. (2016): 1162
- Fried & Kievit (2016): 31

# Session info

```{r}

sessionInfo()

```


